Sailing the High Seas:\\ A Christian Exploration of Piracy

### 2024-04-08 paper.tex
add our definition of piracy to the intro section

>>>>

Before proceeding further into the issue of piracy, it is important to have a grasp of
what piracy means insofar as how this paper interprets it. The dictionary defines piracy
as ``the unauthorized use of another's production, invention, or conception especially in
infringement of a copyright.'' While this covers the technical definition of piracy, this
paper elects to utilize a more wholistic definition. Piracy not only includes the
unauthorized use of someone's work, but it includes the tools and techniques that are
commonly used to accomplish this task such as torrent trackers, VPNs, and torrent clients.
